---
title: "KNN Lab"
author: "Eva Mustafic"
date: "4/5/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(class)
library(caret)
library(e1071) 
library(tidyverse)
library(tidytext)
library(ggwordcloud)
library(gutenbergr)
library(textdata)
library(striprtf)
library(dplyr)
library(readr)
library(knitr)
```

# Task
You left your job as a tracking unstructured text as you wanting to expand your skills into predictive models.  Luckily you landed a job in advertising! Unfortunately have a demanding and totally clueless boss. Clueless meaning that he doesn't understand data science, but he knows he wants it to be used to fix all the company's problems and you are just the data scientist to do it! 

Your company, Marketing Enterprises of Halifax or "MEH" is being beat out by the competition and wants a new way to determine the quality of its commercials. Your boss, Mr. Ed Rooney, would like the company's commercials to seem more like actual TV shows. So he wants you to develop a "machine learning thing" using the company’s internal data to classify when something is a commercial and when it is not. Mr. Rooney believes the company will be able to make more convincing commercials that hold audiences attention if they are more like tv shows and as a result customers will pay more attention, thus buy more of the terrible products "MEH" is supporting (it's a terrible plan, but you have to make a living). 

Given that MEH is producing commercials more or less continuously you know there will be a need to update the model quite frequently, also being a newish data scientist and having a clueless boss you decide to use a accessible approach that you might be able to explain to Mr. Rooney, (given several months of dedicated one on one time), that approach is k-nearest neighbor. 

You'll also need to document your work extensively, because Mr. Rooney doesn't know he's clueless so he will ask lots of "insightful" questions and require lots of detail that he won't understand, so you'll need to have an easy to use reference document. Before you get started you hearken back to the excellent education you received at UVA and using this knowledge outline roughly 15 steps that need to be completed to build this algo for MEH and Ed, they are documented below...good luck. As always, the most important part is translating your work to actionable insights, so please make sure to be verbose in the explanation required for step 15. Think about this questions carefully, what are you really delivering to Mr. Rooney? 

As with the clustering lab, please be prepared to present a five minute overview of your findings. 
 
# Analysis
```{r, warning=FALSE, message=FALSE, echo=FALSE}
#1
#Load in the data, both the commercial dataset and the labels. You'll need to the place the labels on the columns. The dataset "tv_commercialsets-CNN_Cleaned.csv",  is data collected about the features of commercials on CNN. We can try to predict what segments of video are commercials based on their audio and video components. More information on the datasets can be found data.world:
# https://data.world/kramea/tv-commercial-detection/workspace/file?filename=tv_commercial_datasets%2FBBC_Cleaned.csv

#You can use the function colnames() to apply the labels (hint: you might need to reshape the labels to make this work)
setwd("~/Desktop/DS 3220/KNN")
tv <- read.csv("tv_commercial_datasets_CNN_Cleaned.csv") 
cnn <- read.csv("cnn_commmercial_label.csv",  check.names = FALSE,  header=FALSE)

cnn<-dplyr::pull(cnn, V1)
colnames(tv) <- cnn
view(tv)

```

```{r, warning=FALSE, message=FALSE, echo=FALSE}
#2. Determine the split between commercial and non-commercial then calculate the base rate, assume 1 is the commercial label and -1 is the non-commercial label 

ad_split <- function(dat){
  commercial <- filter(dat, `label ` == '1')
  n_comm <- nrow(commercial)
  n_noncomm <- nrow(dat) - nrow(commercial)
  n_total <- nrow(dat)
  n_comm/n_total
}
split <- ad_split(tv)
#There is a 64/36 split
```

```{r, warning=FALSE, message=FALSE, echo=FALSE}
#3. Since there are columns that contain different metrics for the same variable (i.e. any column that ends in 'mn' is the mean of that variable, while any column that ends in 'var' is the variance of that variable), we don't need to keep both, drop all the columns that include var
tv <- select(tv, -ends_with("var"))
view(tv)
```

```{r, warning=FALSE, message=FALSE, echo=FALSE}
#4.  Before we run kNN, sometimes it's good to check to make sure that our variables are not highly correlated. Use the cor() function on 'your_dataframe', label it 'commercial_correlations', and view the data, because remember kNN doesn't work well in high dimensions. 
correlations <- cor(tv)
view(correlations)
```

```{r, warning=FALSE, message=FALSE, echo=FALSE}
#5. Determine which variables to remove, high correlations start around .7 or below -.7 I would especially remove variables that appear to be correlated with more than one variable. List your rationale here:

too_correlated <- c('motion_distr_var')
tv <- tv[,!(names(tv) %in% too_correlated)]

```

We will choose to only get rid of motion_distr_mn because it is highly correlated with two other categories (frame_diff_dist_mn and motion_dist_mn),and among the relationship triangle of those three sets, Motion_distr_mn has the highest correlation values. Therefore motion_distr_mn is the the optimal removal choice.

```{r, warning=FALSE, message=FALSE, echo=FALSE}
#6. Use the index to generate a train and test sets, then check the row counts to be safe. 

set.seed(2702) 

split_index <- sample(nrow(tv), round(0.7 * nrow(tv)))

train <- tv[split_index,] 
test <- tv[!(1:nrow(tv) %in% split_index),] 

true_false <- nrow(test) + nrow(train) == nrow(tv) 
```

```{r, warning=FALSE, message=FALSE, echo=FALSE}
#7 Train the classifier using k = 3, remember to set.seed so you can repeat the output and to use the labels as a vector for the class (not a index of the dataframe)


set.seed(2702) # set seed to be reproducable

tv_labs <- colnames(tv)
tv_3NN <- knn(
  train = train[, tv_labs],
  test = test[, tv_labs],
  cl = train[, "label ", drop = TRUE],
  k = 3,
  use.all = TRUE,
  prob = TRUE
  )
```


```{r, warning=FALSE, message=FALSE, echo=FALSE}
#8 Create a initial confusion matrix using the table function and pass it to a object. (xx <- your confusion matrix)

kNN_res <- table(
  tv_3NN,
  test %>% select(`label `) %>% as_vector()
  )

```

## Initial Confusion Matrix
```{r, warning=FALSE, message=FALSE, echo=FALSE}
#9  Run the confusion matrix function and comment on the model output


confusionMatrix(
  as_factor(tv_3NN), 
  as_factor(test %>% select(`label `) %>% as_vector()), 
  positive = "1", 
  dnn = c("Prediction", "Actual"), 
  mode = "sens_spec"
  )
```

The low p-value  says that the accuracy of our model is significantly greater than the base rate. The sensitivity of the model is 84%, meaning it identifies 84% of the commercials as commercials which is good. The specificity of the model is 53 % meaning it identifies 53% of non-commercials as non-commercials, which is not great. This leads to a positive prediction value that is slightly better than the negative prediction value. We can see that the model predicted 70% of observations were commercials, while only 63% of the observations were actually commercials. That said, the model is "over eager" to predict commercials, and only does so correctly 84% of the time.


```{r, warning=FALSE, message=FALSE, echo=FALSE}
#10 Run the "chooseK" function to find the perfect K, while using sapply() function on chooseK() to test k from 1 to 21 (only selecting the odd numbers), and set the train_set argument to 'commercial_train', val_set to 'commercial_test', train_class to the "label"   column of 'commercial_train', and val_class to the "label" column of 'commercial_test'. Label this  "knn_diff_k_com"


chooseK <- function(k, train_set, val_set, train_class, val_class) {
  set.seed(148759)
  class_knn = knn(train = train_set,
                  test = val_set,
                  cl = train_class,
                  k = k,
                  use.all = TRUE)
  conf_mat = table(class_knn, val_class)
  accu = sum(conf_mat[row(conf_mat) == col(conf_mat)]) / sum(conf_mat)                         
  cbind(k = k, accuracy = accu)
}

# sapply function (k = 1:21)
knn_diff_k_com <- sapply(
  seq(1, 21, by = 2),
  function(x) chooseK(x, 
                      train_set = train[, tv_labs],
                      val_set = test[, tv_labs],
                      train_class = train[, "label ", drop = TRUE],
                      val_class = test[, "label ", drop = TRUE])
  )
```

```{r, warning=FALSE, message=FALSE, echo=FALSE}
#11 Create a dataframe so we can visualize the difference in accuracy based on K, convert the matrix to a dataframe

knn_diff_k_com <- tibble(k = knn_diff_k_com[1,],accuracy = knn_diff_k_com[2,])
```

## Plot for k selection
```{r, warning=FALSE, message=FALSE, echo=FALSE}
#12 Use ggplot to show the output and comment on the k to select.

knn_diff_k_com %>% 
  ggplot() +
  geom_line(aes(x = k, y = accuracy), color = "orange", size = 1.5) +
  geom_point(aes(x = k, y = accuracy), size = 3)
```

k = 9 is the minimum optimal k that has the highest accuracy


```{r, warning=FALSE, message=FALSE, echo=FALSE}
#13 Rerun the model  with the k you selected, assuming it's different. 
set.seed(2702) # set the same seed as in the sapplied function
opt_tv_3NN <-  knn( # run knn with optimal k = 9
  train = train[, tv_labs],
  test = test[, tv_labs],
  cl = train[, "label ", drop = TRUE],
  k = 9,
  use.all = TRUE,
  prob = TRUE
  )
```

## Final Confusion Matrix
```{r, warning=FALSE, message=FALSE, echo=FALSE}
#14 Use the confusion matrix function to measure the quality of the new model.
confusionMatrix(
  as_factor(opt_tv_3NN), 
  as_factor(test %>% select(`label `) %>% as_vector()), 
  positive = "1", 
  dnn = c("Prediction", "Actual"), 
  mode = "sens_spec"
  ) 
```

The low p-value indicates says that the accuracy of our model is significantly greater than the base rate. The sensitivity of the model is 90%, meaning it identifies 90% of the commercials as commercials which is good. The specificity of the model is 49% meaning it identifies 49% of non-commercials as non-commercials, which is not great. This leads to a positive prediction value that is slightly better than the negative prediction value. We can see that the model predicted 75% of observations were commercials, while only 63% of the observations were actually commercials. Model is even more prone to identify a commercial (69% vs 68% for k = 3. It is significantly better than random guess


# Summary
```{r, warning=FALSE, message=FALSE, echo=FALSE}
#15 Summarize the differences in language Mr. Rooney may actually understand. Include a discussion on which approach k=3 or k="optimal" is the better method moving forward for "MEH". Most importantly draft comments about the overall approach and model quality as it relates to addressing the problem proposed by Ed. 
```

If we didn't use any model and randomly guessed something was a commercial, we would be right about 63% of the time. With an optimal knn (knn=9) model, we would be right about 90% of the time.
If we didn't use any model and randomly guessed something was a non-commercial, we would be right about 37% of the time but with an optimal knn model, we would be right about 49% of the time.
The overall accuracy of the optimized model is 74% compared to 72% for our k = 3 knn model. We should use optimized model.


