---
title: "KNN Lab"
<<<<<<< HEAD
author: "Megan Lin"
date: "4/1/2021"
=======
author: "James Powell, Megan Lin, and Eva Mustafic"
date: "4/7/2020"
>>>>>>> e34bb8aacc7a860fceda20d8ac93688b3e82ee7a
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

You left your job as a tracking unstructured text as you wanting to expand your skills into predictive models.  Luckily you landed a job in advertising! Unfortunately have a demanding and totally clueless boss. Clueless meaning that he doesn't understand data science, but he knows he wants it to be used to fix all the company's problems and you are just the data scientist to do it! 

Your company, Marketing Enterprises of Halifax or "MEH" is being beat out by the competition and wants a new way to determine the quality of its commercials. Your boss, Mr. Ed Rooney, would like the company's commercials to seem more like actual TV shows. So he wants you to develop a "machine learning thing" using the company’s internal data to classify when something is a commercial and when it is not. Mr. Rooney believes the company will be able to make more convincing commercials that hold audiences attention if they are more like tv shows and as a result customers will pay more attention, thus buy more of the terrible products "MEH" is supporting (it's a terrible plan, but you have to make a living). 

Given that MEH is producing commercials more or less continuously you know there will be a need to update the model quite frequently, also being a newish data scientist and having a clueless boss you decide to use a accessible approach that you might be able to explain to Mr. Rooney, (given several months of dedicated one on one time), that approach is k-nearest neighbor. 

You'll also need to document your work extensively, because Mr. Rooney doesn't know he's clueless so he will ask lots of "insightful" questions and require lots of detail that he won't understand, so you'll need to have an easy to use reference document. Before you get started you hearken back to the excellent education you received at UVA and using this knowledge outline roughly 15 steps that need to be completed to build this algo for MEH and Ed, they are documented below...good luck. As always, the most important part is translating your work to actionable insights, so please make sure to be verbose in the explanation required for step 15. Think about this questions carefully, what are you really delivering to Mr. Rooney? 

As with the clustering lab, please be prepared to present a five minute overview of your findings. 

```{r}
tv <- read.csv("tv_commercial_datasets_CNN_Cleaned.csv") 
cnn <- read.csv("cnn_commmercial_label.csv",  check.names = FALSE,  header=FALSE)
cnn<-dplyr::pull(cnn, V1)
colnames(tv) <- cnn
view(tv)
```


```{r}
library(dplyr)
library(ggplot2)
library(tidyverse)
```


##Prepare the Data
First, we read in both the clean commercial dataset and the labels for their columns, omitting any NAs. After this we renames the columns of the clean commercial dataset with the names stored in labels. For some reason "shot_length" was the names of the column in this dataset, so we just decided to hard code the names into the columns.
```{r}
#1
#Load in the data, both the commercial dataset and the labels. You'll need to the place the labels on the columns. The dataset "tv_commercialsets-CNN_Cleaned.csv",  is data collected about the features of commercials on CNN. We can try to predict what segments of video are commercials based on their audio and video components. More information on the datasets can be found data.world:
# https://data.world/kramea/tv-commercial-detection/workspace/file?filename=tv_commercial_datasets%2FBBC_Cleaned.csv
#You can use the function colnames() to apply the labels (hint: you might need to reshape the labels to make this work)
cnn_labels <- na.omit(read_csv('cnn_commmercial_label.csv'))
cnn_clean <- na.omit(read.csv('tv_commercial_datasets_CNN_Cleaned.csv'))
names(cnn_clean) <- c('shot_length', 'motion_distr_mn', 'motion_distr_var', 'frame_diff_dist_mn', 'frame_diff_dist_var', 'short_time_energy_mn', 'short_time_energy_var' ,'zcr_mn', 'zcr_var', 'spectral_centroid_mn', 'spectral_centroid_var', 'spectral_roll_off_mn', 'spectral_roll_off_var', 'spectral_flux_mn', 'spectral_flux_var', '	
fundamental_freq_mn', 'fundamental_freq_var', 'motion_dist_mn', 'motion_dist_var', 'label')
View(cnn_clean)
View(cnn_labels)
```

To determine the split, we had to determine the ratio of commercial to total, and based on that, we can deduce the percent of non-commercial entries, and the percentage of both. To do this we created the function ad_split, which prints the ratio of commercial to total entries and ran it on the clean commercial dataset. The split between commercial to non-commercial is 64 percent to 36 percent, respectively.
```{r}
#2. Determine the split between commercial and non-commercial then calculate the base rate, assume 1 is the commercial label and -1 is the non-commercial label 
ad_split <- function(dat){
  commercial <- filter(dat, label == '1')
  n_comm <- nrow(commercial)
  n_noncomm <- nrow(dat) - nrow(commercial)
  n_total <- nrow(dat)
  n_comm/n_total
}
ad_split(cnn_clean)
#There is a 64/36 split
```

To filter out the vars, we create a list of the vars names and saved the dataset over itself without the colums in the vars variable. 
```{r}
#3. Since there are columns that contain different metrics for the same variable (i.e. any column that ends in 'mn' is the mean of that variable, while any column that ends in 'var' is the variance of that variable), we don't need to keep both, drop all the columns that include var
vars <- c('motion_distr_var', 'frame_diff_dist_var', 'short_time_energy_var', 'zcr_var', 'spectral_centroid_var', 'spectral_roll_off_var', 'spectral_flux_var', 'fundamental_freq_var', 'motion_dist_var')
cnn_no_vars <- cnn_clean[,!(names(cnn_clean) %in% vars)]
view(cnn_no_vars)
```

Here we just simply had to run the function cor(), to discover how each column was related to each other to 
```{r}
#4.  Before we run kNN, sometimes it's good to check to make sure that our variables are not highly correlated. Use the cor() function on 'your_dataframe', label it 'commercial_correlations', and view the data, because remember kNN doesn't work well in high dimensions. 
commercial_corelations <- cor(cnn_no_vars)
view(commercial_corelations)
```
We will choose to only get rid of motion_distr_mean because it is highly correlated with two other categories (frame_diff_dist_mn and motion_dist_mn)based on the threshold of .7 and -.7. Therefore motion_distr_mn is the the optimal removal choice. And after this set our data is finished being cleaned, and we are ready to use KNN!
```{r}
#5. Determine which variables to remove, high correlations start around .7 or below -.7 I would especially remove variables that appear to be correlated with more than one variable. List your rationale here:
too_correlated <- c('motion_distr_var')
cnn_final_set <- cnn_no_vars[,!(names(cnn_no_vars) %in% too_correlated)]
```


```{r}
#6. Use the index to generate a train and test sets, then check the row counts to be safe. 
```

```{r}
#7 Train the classifier using k = 3, remember to set.seed so you can repeat the output and to use the labels as a vector for the class (not a index of the dataframe)
```


```{r}
#8 Create a initial confusion matrix using the table function and pass it to a object. (xx <- your confusion matrix)
```

```{r}
#9  Run the confusion matrix function and comment on the model output
```

```{r}
#10 Run the "chooseK" function to find the perfect K, while using sapply() function on chooseK() to test k from 1 to 21 (only selecting the odd numbers), and set the train_set argument to 'commercial_train', val_set to 'commercial_test', train_class to the "label"   column of 'commercial_train', and val_class to the "label" column of 'commercial_test'. Label this  "knn_diff_k_com"
```


```{r}
#10 Run the "chooseK" function to find the perfect K, while using sapply() function on chooseK() to test k from 1 to 21 (only selecting the odd numbers), and set the train_set argument to 'commercial_train', val_set to 'commercial_test', train_class to the "label"   column of 'commercial_train', and val_class to the "label" column of 'commercial_test'. Label this  "knn_diff_k_com"
```

```{r}
#11 Create a dataframe so we can visualize the difference in accuracy based on K, convert the matrix to a dataframe
```

```{r}
#12 Use ggplot to show the output and comment on the k to select.
```

```{r}
#13 Rerun the model  with the k you selected, assuming it's different. 
```

```{r}
#14 Use the confusion matrix function to measure the quality of the new model.
```

```{r}
#15 Summarize the differences in language Mr. Rooney may actually understand. Include a discussion on which approach k=3 or k="optimal" is the better method moving forward for "MEH". Most importantly draft comments about the overall approach and model quality as it relates to addressing the problem proposed by Ed. 
```